---
title: "2019_QB_Breakdown"
author: "Joey Clancy"
date: "8/28/2020"
output: 
  html_document:
    code_download: true
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup and Preprocessing
```{r clear-environment, echo = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE))

# Clear environmet of packages
if (is.null(sessionInfo()$otherPkgs) == FALSE) lapply(paste("package:", names(sessionInfo()$otherPkgs), sep = ""), detach, character.only = TRUE, unload = TRUE)
```

## Load Necessary Packages
```{r package-load, message=FALSE}
library(ggplot2)
library(dplyr)
library(patchwork)
library(kableExtra)
library(plotly)
library(stringr)
```

## Import Data
```{r data-load}
basic_passing <- read.csv("2019_QB_Passing.csv")
adv_accuracy <- read.csv("2019_QB_Accuracy.csv")
adv_air_yards <- read.csv("2019_QB_Air_Yardage.csv")
adv_play_type <- read.csv("2019_QB_Play_Type.csv")
adv_pressure <- read.csv("2019_QB_Pressure.csv")
```

## Clean Data
```{r cleaning}
# Create vector of vars to be converted to factors
names <- c('Player' ,'Tm', 'Pos')

# Create factor variables from all data
basic_passing[,names] <- lapply(basic_passing[,names] , factor)
adv_accuracy[,names] <- lapply(adv_accuracy[,names] , factor)
adv_air_yards[,names] <- lapply(adv_air_yards[,names] , factor)
adv_pressure[,names] <- lapply(adv_pressure[,names] , factor)
adv_play_type[,names] <- lapply(adv_play_type[,names] , factor)

# Get rid of players that don't play the QB position
adv_air_yards <- subset(adv_air_yards, Pos != "wr" & Pos != "")
adv_pressure <- subset(adv_pressure, Pos != "wr" & Pos != "")
adv_play_type <- subset(adv_play_type, Pos != "wr" & Pos != "")

```

## Histogram-Boxplot Pair Function
```{r}
# Creating a function to plot histogram and box plot at the same time
densityBox <- function(data, vbl) {
  density <- ggplot(data = data, mapping = aes(x = {{ vbl }})) +
    geom_density()

  boxplot <- ggplot(data = data, mapping = aes(x = 0)) +
    geom_boxplot(mapping = aes(y = {{ vbl }})) +
    coord_flip()

  density / boxplot
}
```

# Summaries
## Standard Passing Stats
```{r}
summary(basic_passing)
```

## Accuracy
```{r}
summary(adv_accuracy)
```

## Air Yardage
```{r}
summary(adv_air_yards)
```

## Play Type
```{r}
summary(adv_play_type)
```

## Pressure
```{r}
summary(adv_pressure)
```

# Univariate Graphical Analysis
## Numeric Variables

### Completion Rate
```{r}
densityBox(basic_passing, CmpRate)
```

### Touchdown Rate
```{r}
densityBox(basic_passing, TD_Rate)
```

### Interception Rate
```{r}
densityBox(basic_passing, IntRate)
```

### Sack Rate
```{r}
densityBox(basic_passing, SkRate)
```

### 4th Quarter Comebacks
```{r message=FALSE, warning=FALSE}
densityBox(basic_passing, X4QC)
```

### Game Winning Drives
```{r warning = FALSE}
densityBox(basic_passing, GWD)
```

### Yards per Attempt
```{r}
densityBox(basic_passing, Y.A)
```

### Drops
```{r}
densityBox(adv_accuracy, Drops)
```

### Drop Rate
```{r}
densityBox(adv_accuracy, DropRate)
```

### Bad Throws
```{r}
densityBox(adv_accuracy, BadTh)
```

### Bad Throw Rate
```{r}
densityBox(adv_accuracy, BadRate)
```

### On-Target Passes
```{r}
densityBox(adv_accuracy, OnTgt)
```

### On-Target Rate
```{r}
densityBox(adv_accuracy, OnTgtRate)
```

### RPO Plays
```{r}
densityBox(adv_play_type, RPO_Plays)
```

### RPO Yards
```{r}
densityBox(adv_play_type, RPO_Yds)
```

### RPO Pass Attempts
```{r}
densityBox(adv_play_type, RPO_PassAtt)
```

### RPO Pass Yards
```{r}
densityBox(adv_play_type, RPO_PassYds)
```

### RPO Rush Attempts
```{r}
densityBox(adv_play_type, RPO_RushAtt)
```

### RPO Rush Yards
```{r}
densityBox(adv_play_type, RPO_RushYds)
```

### Play Action Pass Attempts
```{r}
densityBox(adv_play_type, PA_PassAtt)
```

### Play Action Rush Attempts
```{r}
densityBox(adv_play_type, PA_PassYds)
```

### Intended Air Yards
```{r}
densityBox(adv_air_yards, IAY)
```

### Intended Air Yards per Attempt
```{r}
densityBox(adv_air_yards, IAY.PA)
```

### Completed Air Yards
```{r}
densityBox(adv_air_yards, CAY)
```

### Completed Air Yards per Completion
```{r}
densityBox(adv_air_yards, CAY.Cmp)
```

### Completed Air Yards per Pass Attempt
```{r}
densityBox(adv_air_yards, CAY.PA)
```

### Pass Yards After Catch
```{r}
densityBox(adv_air_yards, YAC)
```

### Yards After Catch per Completion
```{r}
densityBox(adv_air_yards, YAC.Cmp)
```

### Pocket Time
```{r}
densityBox(adv_pressure, PktTime)
```

### Blitz Count
```{r}
densityBox(adv_pressure, BltzCount)
```

### Times Hurried
```{r}
densityBox(adv_pressure, Hrry)
```

### Times Hit while Passing
```{r}
densityBox(adv_pressure, Hits)
```

### Times Pressured
```{r}
densityBox(adv_pressure, Prss)
```

### Pressure Rate
```{r}
densityBox(adv_pressure, PrssRate)
```

### Scrambles
```{r}
densityBox(adv_pressure, Scrm)
```

### Yards per Scramble
```{r warning=FALSE}
densityBox(adv_pressure, Yds.Scr)
```


























































































